### 2012-01-21 docs/SDC/sdc.tex
lots of updating.  Explicitly write out the form of I for species for the 3 different species_pred_types.

\subsection{SDC version}
In the SDC version, the VODE integration at the end of an SDC
iteration is responsible for updating all the thermodynamic quantities
\{$\rho$, $(\rho h)$, and $(\rho X_k$)\}, including both the advective
fluxes (incorporated via a piecewise constant advective flux source
term) and the reactions.  This provides a much stronger coupling between
the physical processes.  In particular, our system now looks like:
\begin{eqnarray}
\frac{d(\rho X_k)}{dt} &=& \rho \omegadot_k(\rho,X_k,T) + A_{\rho X_k} \\
\frac{d(\rho h)}{dt}   &=& \rho \Hnuc + A_{\rho h}
\end{eqnarray}
Here, $A_{\rho X_k}$ and $A_{\rho h}$ are piecewise-constant (in time)
approximations to the change in ${\rho X_k}$ and ${\rho h}$ (respectively)
due to the advection.  These are constructed by calling {\tt density\_advance}
and {\tt enthalpy\_advance} in \maestro\ and passed into the network solver
during the reaction step.  These terms approximate the following:
\begin{eqnarray}
A_{\rho X_k} &=&  \left [- \nabla \cdot (\rho X_k \Ub) \right ]^{n+1/2} \\
A_{\rho h}   &=&  \left [- \nabla \cdot (\rho h U) + \frac{Dp_0}{Dt} \right ]^{n+1/2}
\end{eqnarray}
The construction of the interface states used in the advective terms
uses an iteratively-lagged approximation to the reaction source terms
in the interface prediction.  This explicitly couples the reaction
process to the advection process.

@@

At the end of the integration, we define 
\begin{eqnarray}
I_{\rho X_k} &=& \frac{(\rho X_k)^\mathrm{new} - (\rho X_k)^\mathrm{old}}{\Delta t} - A_{\rho X_k} \\
I_{\rho h}  &=& \frac{(\rho h)^\mathrm{new} - (\rho h)^\mathrm{old}}{\Delta t} - A_{\rho h}
\end{eqnarray}
These terms are used as the source terms for the advection step in the
next SDC iteration.

>>>>

\subsection{SDC version}
In the SDC version, the VODE integration at the end of an SDC
iteration is responsible for updating all the thermodynamic quantities
\{$\rho$, $(\rho h)$, and $(\rho X_k$)\}, including both the advective
fluxes (incorporated via a piecewise constant advective flux source
term) and the reactions.  This provides a much stronger coupling between
the physical processes.  In particular, our system now looks like:
\begin{eqnarray}
\frac{d(\rho X_k)}{dt} &=& \rho \omegadot_k(\rho,X_k,T) + A_{\rho X_k} \\
\frac{d(\rho h)}{dt}   &=& \rho \Hnuc + A_{\rho h}
\end{eqnarray}
Here, $A_{\rho X_k}$ and $A_{\rho h}$ are piecewise-constant (in time)
approximations to the change in ${\rho X_k}$ and ${\rho h}$ (respectively)
due to the advection.  These are constructed by calling {\tt density\_advance}
and {\tt enthalpy\_advance} in \maestro\ and passed into the network solver
during the reaction step.

\subsubsection{Advective Update}

In the advective update, our goal is to compute $A_{\rho X_k}$ and
$A_{\rho h}$.  These terms approximate the following:
\begin{eqnarray}
A_{\rho X_k} &=&  \left [- \nabla \cdot (\rho X_k \Ub) \right ]^{n+1/2} \\
A_{\rho h}   &=&  \left [- \nabla \cdot (\rho h U) + \frac{Dp_0}{Dt} \right ]^{n+1/2}
\end{eqnarray}
The construction of the interface states used in the advective terms
uses an iteratively-lagged approximation to the reaction source terms
($I_{\rho X_k}$ and $I_{\rho h}$, see below) in the interface
prediction.  This explicitly couples the reaction process to the
advection process.

\subsubsection{Final Update}

@@

At the end of the integration, we define $I_{\rho X_k}$ and $I_{\rho
  h}$.  The actual form of these depends on what we are predicting.
We note that we only need $I_{\rho X_k}$ and $I_{\rho h}$ for the
prediction of the interface states, not the final conservative update.
That is because all we need from the advection solver is the
approximation to $A_{\rho X_k}$ and $A_{\rho h}$, not the final
updated state.

\paragraph{Species Source Terms.}
For the species prediction, the form of $I_{\rho X_k}$ depends on
{\tt species\_pred\_type} (see \S \ref{sec:pred:density}):  
\begin{itemize}
\item {\tt species\_pred\_type} = 1 (predict $\rho'$ and $X_k$)
%
\begin{equation}
I_{\rho X_k} = \frac{1}{\rho^{n+\half}} \left [ 
      \frac{(\rho X_k)^\mathrm{new} - 
            (\rho X_k)^\mathrm{old}}{\Delta t} - A_{\rho X_k}  \right ]
\end{equation}

\item {\tt species\_pred\_type} = 2 (predict $\rho'$ and $(\rho X_k)$)
%
\begin{equation}
I_{\rho X_k} = \frac{(\rho X_k)^\mathrm{new} - (\rho X_k)^\mathrm{old}}{\Delta t} - A_{\rho X_k} 
\end{equation}

\item {\tt species\_pred\_type} = 3 (predict $\rho$ and $X_k$)
%
\begin{equation}
I_{\rho X_k} = \frac{1}{\rho^{n+\half}} \left [ 
      \frac{(\rho X_k)^\mathrm{new} - 
            (\rho X_k)^\mathrm{old}}{\Delta t} - A_{\rho X_k}  \right ]
\end{equation}

We note that there is no $I$ term for $\rho$ or $\rho'$ prediction, since
the density evolution equation does not have a reaction source term.

\paragraph{Enthalpy Source Terms.}
For the enthalpy prediction, the form of $I_{\rho h}$ depends on
{\tt enthalpy\_pred\_type} (see \S \ref{sec:pred:enthalpy}).:
\begin{itemize}
\item {\tt enthalpy\_pred\_type} = 1 \\
not right -- should be pert form
\begin{equation}
I_{\rho h}  = \frac{(\rho h)^\mathrm{new} - (\rho h)^\mathrm{old}}{\Delta t} - A_{\rho h}
\end{equation}
\end{itemize}

This is done in {\tt advance.f90} just after the call to {\tt react\_state},
stored in the \multifab\ {\tt intra}.

These terms are used as the source terms for the
advection step in the next SDC iteration.
